My title

### 2023-02-11 outputs/paper/paper.qmd
Add more example scripts and add cross-references to quorto

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
bibliography: references.bib
---

```{r}
#| include: FALSE

knitr::opts_chunk$set(echo = TRUE)

@@

You can and should cross-reference sections and sub-sections. For instance, Section \@ref(data). Quarto automatically makes the sections lower case and adds a dash to spaces to generate labels, for instance, Section \@ref(first-discussion-point).

# Data

@@

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

@@

## First discussion point

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

@@

You can and should cross-reference sections and sub-sections. For instance, @sec-data and @sec-first-point.

# Data {#sec-data}

@@

@@

## First discussion point {#sec-first-point}
